Lavaging Camera Geometry in Deep Neural Network Learning for Image Understanding

### 2018-06-19 dissertation.tex
Updates from ShareLaTeX
update title and abstract

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{xspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{memhfixc}
\usepackage{algorithm2e, algorithmic}
\usepackage{soul}
\usepackage{miscstyle}

\newcommand{\disstitle}{Camera Geometry Detection and Use for Image
Understanding}

\usepackage[pdfauthor={Menghua Zhai},
            pdftitle={\disstitle},
            bookmarks=false,
            bookmarksnumbered=true,
            bookmarksopen=true,
            breaklinks=true,
            letterpaper=true,
            linktocpage,
            pagebackref=true]{hyperref}

@@

\author{Menghua Zhai}
\title{\disstitle}

\abstract
{
  \SingleSpacing
  Camera geometry is one of the fundamental elements in computer vision.
  It plays an essential role in many applications like depth estimation
  and image mensuration. 
  %
  In recent years, the rise of deep neural networks (DNNs) had changed
  the game in many computer vision areas, their ability of abstracting
  high-level semantic knowledges makes a lot of hard challenges
  solvable. 
  %
  This thesis mainly explores the possibility of combining camera
  geometry and DNNs. That is 1) Detecting camera geometry using DNNs,
  and 2) Training DNNs with camera geometric information.  Our work
  includes two research targets: The first part of this thesis focuses
  on camera geometry detection with DNNs, and the rest of it
  demonstrates how camera geometry can boost the learning of DNNs.
  %
  The primary contribution of this thesis is to explore the relation
  between camera geometry and image semantics, and bridge the gap
  between these two research domains, which provides us new ways for
  both camera calibration and deep neural network training.
}
\keywords{ camera geometry, deep neural networks, computer vision}

@@

\inject{introduction}
%\inject{mcmc}
%\inject{background}
%\inject{discussion}

>>>>

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{import}
\usepackage{xspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{memhfixc}
\usepackage{algorithm2e, algorithmic}
\usepackage{soul}
\usepackage{multirow}
\usepackage{miscstyle}

\usepackage[pdfauthor={Menghua Zhai},
            pdftitle={dissertation},
            bookmarks=false,
            bookmarksnumbered=true,
            bookmarksopen=true,
            breaklinks=true,
            letterpaper=true,
            linktocpage,
            pagebackref=true]{hyperref}

@@

\author{Menghua Zhai}
\title{Lavaging Camera Geometry in Deep Neural Network Learning for Image Understanding}

\abstract
{ \SingleSpacing
In recent years, Deep Neural Networks (DNNs) have proven to be very
successful in many computer vision areas. Among the most popular
training techniques, supervised learning is wildly used for DNN
training and easy to implement. However, successful supervised
learning approaches are sensitive to the quality of data
annotations. In some applications like overhead image segmentation and
transient attributes estimation, data with noise-free annotation is
either limited in quantity or technically difficult to acquire.
In this thesis, we use domain adaptation and weak supervision to
address this problem. Our methods focus on lavaging the camera
geometric information to deal with the challenges caused by the lack
of noise-free annotations during DNN training.
Since the camera geometry affects the way that images manifest
objects/scenes, it is possible to exploit the relation between the
camera geometry and image semantics to understand images better.
Our approach consists of two parts: 1) we explore new methods
to estimate the camera geometric information from images, and 2) 
we propose novel algorithms that lavages the camera geometry to train
deep neural networks.
The primary contribution of our thesis is to relate the camera
geometry and image semantics through deep neural networks. Our
discoveries can provide researchers new insights for both camera
calibration and DNN training.
}
\keywords{ camera geometry, deep neural networks, computer vision}

@@

\inject{introduction}
%\inject{background}

%\inject{mcmc}
%\inject{fasthorizon}
%\inject{crosstransf}
%\inject{whenwhere}

%\inject{discussion}

### 2018-06-19 junk.tex
update title and abstract

>>>>

abstract
Camera geometry is one of the fundamental elements in computer vision.
It plays essential roles in many applications like depth estimation
and image mensuration.
%
In recent years, the rise of deep neural networks (DNNs) had changed
the game in many computer vision areas, their ability of abstracting
high-level semantic knowledges makes a lot of hard challenges
solvable.
%
This thesis mainly explores the possibility of combining camera
geometry and DNNs. That is 1) Detecting camera geometry using DNNs,
and 2) Training DNNs with camera geometric information.  Our work
includes two research targets: The first part of this thesis focuses
on camera geometry detection with DNNs, and the rest of it
demonstrates how camera geometry can boost the learning of DNNs.
%
The primary contribution of this thesis is to explore the relation
between camera geometry and image semantics, and bridge the gap
between these two research domains, which provides us new ways for
both camera calibration and deep neural network training.
